%-------------------------
% Resume in Latex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[stable]{footmisc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\cfoot{\textit{\small Page \thepage \hspace{1pt} of 3}}
\rfoot{\textit{\small Last updated on {\the\month}  / {\the\year}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat?s bookmarks
    pdftoolbar=true,        % show Acrobat?s toolbar?
    pdfmenubar=true,        % show Acrobat?s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Samer Makary - Resume},    % title
    pdfauthor={Samer Makary},     % author
    pdfsubject={Samer Makary - Resume},   % subject of the document
    pdfcreator={Samer Makary},   % creator of the document
    pdfproducer={Samer Makary}, % producer of the document
    pdfkeywords={}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=blue           % color of external links
}
%-------------------------------------------
%%%%%%  Resume STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Samer Makary} & \href{mailto:samer.samy.nazzir@gmail.com}{samer.samy.nazzir@gmail.com}\\
  \href{https://github.com/samer-makary}{https://github.com/samer-makary} & Atlanta, USA\\
\end{tabular*}


%-----------PROFESSIONAL PROFILE-----------------
\section{Professional Profile}
Full-stack Software Engineer with more than 10 years of experience building API/Client-first services development.\\
In-depth experience in multiple domains, including music/audio broadcast, low-latency (high-throughput) distributed systems and caches, real-time ad-delivery services, and location-based and data-mobilization software solutions.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon.com, Inc.}{Jan 2020 - Present}
      {Software Development Engineer II}{}
      \resumeItemListStart
		\resumeItem{Ads Filtering \& Eligibility Services}
          {Designed a globally-accessible Ad Eligibility API handling hundreds of transactions per second using API Gateway, Lambda, and \textbf{DynamoDB GlobalTables}, delivering cross-regional distributed solution. \\
          -- Developing next generation Ads Filtering service using various technologies such as AWS ECS and SQS.}
		\resumeItem{Amp}
          {Amazon Music's \href{https://techcrunch.com/2022/03/08/amazon-launches-a-live-radio-app-amp-which-lets-you-play-dj-with-the-amazon-music-catalog/}{Amp} in an infinite-dial digital radio broadcast mobile application. Amp allows users to create a show, go live, play music, and take in call-in guests all with simple flow and within minutes.\\
          -- Lead engineer developing Amp Android app and migrating Amp iOS app to hybrid \textbf{ReactNative}-based architecture with native core components in both \textbf{iOS Swift} and \textbf{Android Kotlin}.\\
          -- Team leader of Call-in experience full-stack development maintaining iOS/Swift client and backend system using AWS Lambda, Chime APIs, and \textbf{Elastic-Containers on Fargate} microservices.\\
          -- Led a team of engineers to deliver the first public version of the Creator Studio iOS app implemented using \textbf{Swift} and AWS AppSync \textbf{GraphQL} entirely from the grounds-up.}          
		\resumeItem{FenixSPService}
          {Core orchestration engine that serves \href{https://advertising.amazon.com/solutions/products/sponsored-products}{Sponsored-Products Ads} on Amazon.com retail website and mobile app worldwide. Fenix is a high-throughput low-latency real-time distributed service that delivers curated ads per user on Amazon.com pages and apps. Utilizing \textbf{Java} and \textbf{Spring MVC}.}
        \resumeItem{FenixSPService on Native AWS (NAWS)}
          {Delivered the first proof-of-concept demonstrating the ability to boot up \texttt{FenixSPService} on the public/native offering of AWS ecosystem.\\
          -- Identified +20 technical blockers, led team of engineers to develop simple workaround solutions, and eventually provided a risk-mitigation path for the actual migration and deployment of the service.\\
          -- Launching \texttt{FenixSPService} on Native AWS was later featured in \href{https://youtu.be/BS4MPpEO66I?t=1067}{AWS re:Invent 2021 - Under the hood at Amazon Ads}.}
        \resumeItem{DevOps and OnCall}
          {Participate in on-call and deployment shepherd rotations. Improve pipelines and monitoring to implement best practices of CI/CD.}
	\resumeItemListEnd

    \resumeSubheading
      {Webalo, Inc.}{Jul 2016 - Dec 2019}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{HTML Toolkit}
          {Designed the architecture for a new HTML-based platform-agnostic UI widget rendering toolkit.\\
          -- Led a team of engineers to develop and migrate \href{https://www.webalo.com/platform.php}{Webalo}'s User Agent applications to the new toolkit and retire the Java Canvas-based toolkit.
          Utilizing TypeScript and Web Components in \textbf{Angular 7}, \textbf{Bootstrap}, and JavaScript/CSS.}
        \resumeItem{CI/CD}
          {Automated system build, execution of integration and end-to-end tests, and binaries distribution through using Git Hooks, \textbf{Jenkins}, and Shell scripting.}
        \resumeItem{Unit \& Integration testing}
          {Spearheaded the effort to set up and design system testing framework for developing integration tests.\\
          -- Utilizing \textbf{TestNG} and \textbf{Mockito} for module testing and \textbf{Selenium} for end-to-end testing.}
      \resumeItemListEnd

    \resumeSubheading
      {Google, Inc.}{Aug 2015 - Nov 2015}
      {Software Engineering Intern}{}
      \resumeItemListStart
        \resumeItem{Sandlot}
          {As part of the \href{https://careersonair.withgoogle.com/events/insidegtech}{G-Tech team}, integrated sentiment prediction into Google's partners management tool. Responsible for the design and implementation of the new feature using \textbf{Python} and \textbf{AngularJS}.}
      \resumeItemListEnd
      
\pagebreak

    \resumeSubheading
      {Wireless Stars, LLC}{Oct 2013 - May 2015}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{ARTS}
          {System for road traffic estimation based on user cell-phone data analytics. Building \textbf{Android} SDK for location and sensor data collection.\\
          Collaborating with research team on developing production ready algorithms and modules for data processing back-end system using \textbf{Spring Boot} and data pipeline through Apache Camel.\\
          Responsible for implementation and testing of \textbf{Kalman-filter} user speed estimator.\\
          Utilized \href{https://postgis.net/}{PostGIS} to implement spatial queries consumed by various modules of the system.\\
          Implemented \textbf{Android} app that uses traffic SDK to push data to the back-end and query the system for estimated traffic state. The application was used by business team for demo/presentation and by the research team for system evaluation.}
        \resumeItem{EYE360}
          {Augmented reality application providing bi-directional user interaction built using \textbf{Unity3D} and Qualcomm \textbf{Vuforia} SDK}
      \resumeItemListEnd

    \resumeSubheading
      {B-Yond}{}
      {Consultant Engineer}{}
      \resumeItemListStart
		\resumeItem{National ID Segmentation}
          {Designed and implemented customer license management in \textbf{Python using JWT}, obfuscation, and elliptic curve cryptography.\\
          Designed run-time transaction management using symmetric key cryptography.\\
          Advised ML and junior engineers on deployment strategies and post deployment monitoring, support, and CI/CD.}
	\resumeItemListEnd	
      
    \resumeSubheading
      {Coptic Academy, NGO}{}
      {Part-time Back-end Engineer}{}
      \resumeItemListStart
        \resumeItem{R\&D}
          {Evaluated the use of technologies like HashiCorp and JWT for implementing client/service secured communications.}
        \resumeItem{CPlanner}
          {Maintained RESTful data-serving back-end for \href{https://play.google.com/store/apps/details?id=org.copticacademy}{Coptic Planner mobile} app. Responsibilities include REST API extension using \textbf{Spring Boot} and Hibernate, deployment to production server and bug troubleshooting/fixing. Optimization of back-end operations and SQL queries.}
        \resumeItem{CMentor}
          {Set up, designed, and implemented RESTful back-end for \href{https://play.google.com/store/apps/details?id=org.copticacademy.CopticMentor}{Coptic Mentor mobile} app using Spring Boot and \textbf{Hibernate}.}
        \resumeItem{Batch-processor}
          {Designed and implemented data batch-processor driven by cron jobs for consuming system data, via optimized SQL queries, and delivering custom notification in \textbf{Java} and \textbf{shell scripts}.}
      \resumeItemListEnd

    \resumeSubheading
      {Alexandria University}{Sep 2012 - Jan 2013}
      {Teaching Assistant}{}
      \resumeItemListStart
        \resumeItem{In Special Scientific Program (SSP)}
          {Teaching Introduction to Databases and Numerical Analysis courses.}
      \resumeItemListEnd

    \resumeSubheading
      {Innuva, IT}{Jul 2011 - Oct 2011}
      {Game Developer Trainee}{}
      \resumeItemListStart
        \resumeItem{3D shooting game}
          {Game design and implementation using \textbf{Unity3D} game engine. The game logic is being implemented using JavaScript for Unity3D.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
      
\pagebreak

%-----------TOOLS & FRAMEWORKS-----------------
\section{Tools \& Frameworks \footnotemark}
  \footnotetext{Technologies are listed in decreasing order of experience.}

  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Java -- Swift -- Python -- TypeScript -- HTML/JavaScript/CSS -- SQL}
    \resumeSubItem{Frameworks}{iOS -- ReactNative -- Spring MVC/Boot -- Bootstrap -- Angular 7 -- Unity3D -- Android}
    \resumeSubItem{CI/CD}{CDK-- Jenkins -- TestNG -- Selenium -- Mockito/PowerMock -- Jasmine/Karma}

    \vspace{5pt}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Alexandria University, Faculty of Engineering}{Sep 2007 -- Jul 2012}
      {B.Sc. Computer and Systems Engineering}{}
  \resumeSubHeadingListEnd
  
  
%-----------CONTINUOUS EDUCATION-----------------
\section{Continuous Education \footnotemark}
  \footnotetext{Certificates are available upon request.}
   \resumeSubHeadingListStart
	\resumeSubItem{Architecture and Developing on AWS}{AWS Hands-on Training}
	\resumeSubItem{DevOps on AWS}{AWS Hands-on Training}
	\resumeSubItem{Security Engineering on AWS}{AWS Hands-on Training}
    \resumeSubItem{Programming Languages}{Coursera - Washington Uni}
    \resumeSubItem{Introduction to Functional Programming in Scala}{Coursera}
    \resumeSubItem{Applied Cryptography}{Udacity}
    \resumeSubItem{Introduction to Cryptography}{Coursera - Stanford}
    \resumeSubItem{Introduction to Recommender Systems}{Coursera - Uni of Minnesota}
    \resumeSubItem{Algorithms Design and Analysis}{Coursera - Stanford}
    \resumeSubItem{CSMM.102x Machine Learning}{Edx - ColumbiaX}
    \resumeSubItem{CSMM.101x Artificial Intelligence}{Edx - ColumbiaX}
    \resumeSubItem{Introduction to AI for Robotics}{Udacity}
    \resumeSubItem{Machine Learning}{Coursera}
    \resumeSubItem{Coding the Matrix}{Coursera}
    \resumeSubItem{Scalable Machine Learning}{Edx}

    \vspace{5pt}
  \resumeSubHeadingListEnd


%--------ACADEMIC PROJECTS------------
%\section{Academic Projects}
%  \resumeSubHeadingListStart
%	\item \textbf{Documents Clustering with Semantics-based Similarity} -- [Java]\\ 
%	Developing a Semantic-based similarity metric for Arabic documents. The approach was then used for clustering news articles using different clustering algorithms like DBSCAN and \href{http://www.sciencedirect.com/science/article/pii/S0031320308003701}{Mitosis}.
%	\item \textbf{Split TCP} -- [Java]\\
%	Implementing \href{http://www.cs.ucr.edu/~krish/splittcp.pdf}{Split TCP} protocol for wireless ad-hoc networks to improve performance.	
%	\item \textbf{eVoting System} -- [C++ over Linux]\\
%	Implementing the principles of the Application Layer HTTP client/server requests using Socket connection over TCP and UDP. 
%	\item \textbf{Machine Learning} -- [MATLAB]\\
%	Implementing techniques and algorithms like Linear and Logistic Regression, Neural Networks, K-Means clustering, and Gaussian anomaly detection.
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}